Synthesizing Slow Motion Periodic Videos via Circular Coordinate Reshuffling And Voting

### 2018-01-17 Paper/paper.tex
Committing more changes

\begin{algorithm}[t]
  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
  \begin{algorithmic}[1]
    \Procedure{ReorderVideo}{$X$, $L$, weighted, median} \\
    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames, an $N \times 3WH$ matrix}
    \State ($\theta, d) \gets$ CIRCCOORDS($X, L$)
    \State Perform SVD $X = USV^T$, $\hat{X} \gets US \in \mathbb{R}^{N \times (N-1)}$
    \State $\hat{Y} \gets SW_d[\hat{X}[n]] \in \mathbb{R}^{M \times (N-1)d}$, $M = N-d+1$
    \If {median}
        \State Order $\hat{Y}$ by $\theta$, line up each window in time, and linearly interpolate coordinates of $\hat{Y}$
        \State Do median consensus on aligned pixels of $\hat{Y}V^T$ \label{algline:medianconsensus}
    \Else
        \State Order first frames in each window by $\theta$
    \EndIf
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
    \caption{Laplacian Circular Coordinates}
    \begin{algorithmic}[1]
    \Procedure{CircCoords}{$X$, $L$}
    \State $\hat{X} \gets $ image pyramid level $L$ of $X$
    \State Perform SVD $\hat{X} = USV^T$, $Y \gets US \in \mathbb{R}^{N \times (N-1)}$
    \State $y \gets$ 1D ISOMAP($Y$) \cite{tenenbaum2000global}
    \State $d \gets$ fundamental period estimate of $y$ \cite{Mcleod05asmarter}
    \State $Z \gets SW_{d}[Y[n]] \in \mathbb{R}^{M \times (N-1)d}$, $M = N-d+1$

@@

We now describe our algorithm in several stages.  Throughout our discussion, we assume we are dealing with 3 channel color videos.  For a frame resolution of $W \times H$, each frame can be thought of as a Euclidean vector in $\mathbb{R}^{W \times H \times 3}$.  Algorithm~\ref{alg:videoreordering} shows the full details of our method in pseudocode.

@@

\begin{equation}
SW_{d, \tau}[X(t)] = \left[ \begin{array}{c} X(t) \\ X(t + \tau) \\ \vdots \\ X(t + (d-1)\tau)  \in \mathbb{R}^{3WHd} \end{array} \right]
\end{equation}

@@

\subsection{Cycle Reordering}
\label{sec:cyclereordering}

>>>>

\begin{algorithm}[t]
  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
  \begin{algorithmic}[1]
    \Procedure{ReorderVideo}{$X$, $L$, weighted, median} \\
    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames, an $N \times 3WH$ matrix}
    \State ($\theta, d) \gets$ CIRCCOORDS($X, L$)
    \State Perform SVD $X = USV^T$, $\hat{X} \gets US \in \mathbb{R}^{N \times N}$
    \State $\hat{Y} \gets SW_d[\hat{X}[n]] \in \mathbb{R}^{M \times N \times d}$, $M = N-d+1$
    \If {median}
        \State Order $\hat{Y}$ by $\theta$, line up each window in time, and linearly interpolate coordinates of $\hat{Y}$
        \State Do median consensus on aligned pixels of $\hat{Y}V^T$ \label{algline:medianconsensus}
    \Else
        \State Order first frames in each window by $\theta$
    \EndIf
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
    \caption{Laplacian Circular Coordinates}
    \begin{algorithmic}[1]
    \Procedure{CircCoords}{$X$, $L$}
    \State $\hat{X} \gets $ image pyramid level $L$ of $X$
    \State Perform SVD $\hat{X} = USV^T$, $Y \gets US \in \mathbb{R}^{N \times N}$
    \State $y \gets$ 1D ISOMAP($Y$) \cite{tenenbaum2000global}
    \State $d \gets$ fundamental period estimate of $y$ \cite{Mcleod05asmarter}
    \State $Z \gets SW_{d}[Y[n]] \in \mathbb{R}^{M \times N \times d}$, $M = N-d+1$

@@

We now describe our algorithm in several stages.  Throughout our discussion, we assume we are dealing with 3 channel color videos.  For a frame resolution of $W \times H$, each frame can be thought of as a Euclidean vector in $\mathbb{R}^{W \times H \times 3}$.  For a video with $N$ frames, we flatten each frame to a 1D vector and stack them row wise along an $N \times 3WH$ matrix $X$.  Whenever we perform a linear operation on all of the pixels at once, we can use the SVD $X = USV^T$ to reduce memory and computational costs by working with $US$ in place of $X$, which is in $N$ dimensions instead of $3WH \gg N$ (similar processing was done in \cite{turk1991eigenfaces} and \cite{tralie2017quasi}).  The only nonlinear operation is the median operation (Section~\ref{sec:cyclereordering}), and we project back into pixel space using $V^T$ before taking the median. Algorithm~\ref{alg:videoreordering} shows the full details of our method in pseudocode.

@@

\begin{equation}
SW_{d, \tau}[X(t)] = \left[ \begin{array}{c} X(t) \\ X(t + \tau) \\ \vdots \\ X(t + (d-1)\tau)  \end{array} \right] \in \mathbb{R}^{3WHd}
\end{equation}

@@

\subsection{Cycle Reordering And Median Voting}
\label{sec:cyclereordering}
